Generalised Management Strategy Evaluation: modelling biodiversity and food security

### 2020-05-12 notebook/presentation/GMSE_presentation.Rmd

- Formalisation and study of conflict and cooperation between rational decision-makers
- Compatibile with agent-based modelling
- Can suggest management strategiesand be used to understand stake-holder actions
- Conceptual unification

@@

>>>>

- Formalisation and study of conflict and cooperation between rational decision-makers
- Compatibile with agent-based modelling
- Can suggest management strategies and be used to understand stake-holder actions
- Conceptual unification

@@

![](meadow.jpg)

[Wing-Chi Poon](https://commons.wikimedia.org/wiki/File:Mist_Covering_a_Meadow_under_Forest_Encroachment.jpg)
